Heavy inextensible strings in the Schwarzschild geometry

### 2024-10-31 weighted_string.Rmd
use approxfun

$$
\int_{p_1}^{p_2}\left[\left(\frac{\left(r'\right)^2}{1-2M/r} + r^2\right)^\frac{1}{2}
+\lambda\left(\frac{\left(r'\right)^2}{1-2M/r} + r^2\right)^\frac{1}{2}
\left(1+\lambda(1-\sqrt{1-2M/r})\right)
\right]d\phi
$$

@@

size <- 5
plot(c(-size,size),c(-size,size),type="n",asp=1)
th <- seq(from=0,to=2*pi,len=100)
points(cos(th),sin(th),type='l')  # event horizon
points(string(r0=1.4,lambda= 0,angles=seq(0,2,0.01)),type='l')
for(l in seq(from=-0.1,to=-1.4,by=-0.1)){
    points(string(r0=1.4,lambda=l,angles=seq(0,pi/2,0.01)),type='l')
}
```

>>>>

$$
\int_{p_1}^{p_2}\left[\left(\frac{\left(r'\right)^2}{1-2M/r} + r^2\right)^\frac{1}{2}
+\lambda\left(\frac{\left(r'\right)^2}{1-2M/r} + r^2\right)^\frac{1}{2}
\left(1-\sqrt{1-2M/r}\right)
\right]d\phi
$$

@@

lambda <- seq(from = -0.05, to = -1.7, by = -0.1)
f <- approxfun(
    c(0,-0.1,-0.2,-0.5, -0.7, -1,  -1.4,     -1.6,-1.7),
    c(2.4,2.4, 2.1,1.5,   1.5, 1.1,  0.63, 0.3,0)
)

plot(lambda,f(lambda))

size <- 2
par(pty="s")
plot(NA,type="n",asp=1,xlim=c(-size,size),ylim=c(-size,size))
th <- seq(from=0,to=2*pi,len=100)
points(cos(th),sin(th),type='l')  # event horizon

for(l in lambda){
    points(string(r0=1.2,lambda=l,angles=seq(0,f(l),0.01)),type='l')
}

segments(1.2,0,4,0)
docolour <- function(lambda,...){
    points(string(r0=1.2,lambda=lambda,angles=seq(0,f(lambda),0.01)), type='l', lwd=3, ...)
}
docolour(-0.05,col='blue')
docolour(-0.7,col='green')
docolour(-1.4,col='red')
points(1.2,0,pch=16)

```
